A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\medskip
{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction. The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).

>>>>

\medskip
{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM). Depending on the context in which MOR is used, it can be simply referred as `dimensionality reduction'. The definition of MOR also depends on the context in which it is used, but it suffices to state that MOR's are ale to captures essential features of a system, structure or parameter \cite{Schilders2008}. This implies that an original system exists with more detailed information. Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).
